---
title: "Indian Recipes"
---

## Section 1: Dataset

This is an examination of an Indian Food Dataset containing dishes from various states and regions of India.

I chose this dataset because I am Indian American, and I love looking at food. I thought it would be interesting to analyze the regions and states of India and how their food differentiates and varies. This was also a really lovely, laid-out dataset with flavor profiles and course types.

I found this dataset by searching food on [Kaggle](https://www.kaggle.com/datasets/nehaprabhavalkar/indian-food-101/datandefined). It caught my eye, and I wanted to analyze it. This is the `indian_food.csv` dataset.

```{r imports, include=FALSE}
library(rvest)
library(tidyverse)
library(janitor)
library(readr)
library(dplyr)
library(gt)
library(scales)
library(ggthemes)
library(extrafont)
library(knitr)
loadfonts(device = "win")
```

```{r loadingdata}
india <- read.csv("indian_food.csv")
glimpse(india)
```

The Indian Food dataset that we are working with has 225 food entries and 9 columns of characteristics.

Throughout this analysis, we will break down many columns to see similarities and differences between the regions and states.

**Disclaimer**: Food is very various and infinite. This is not a comprehensive list of Indian Food by any means, so we are doing a surface-level analysis. Anything discovered here is taken with a grain of salt because the sample size for everything is not greater than 10% of the whole population.

## Section 2: Exploratory Data Analysis

Lets take a look at this data. I want to do this my looking at many questions that I want answers to. We can do this by looking at graphs.

1.  What is the distribution of dishes from each state? What about each region?

```{r q1, warning=FALSE, results='hide'}
states <- india |> 
  group_by(state) |> 
  summarize(
    n = n()
  ) |> 
  mutate(state = ifelse(state == "-1", "Other", state
                       )
         ) |> 
  arrange(state) |> 
  rename(count = n)
```

```{r}
ggplot(states, mapping = aes(x=state, 
                             y=count)) +
  geom_col() +
  labs(title = "Number of Dishes per State in Dataset",
       x = "State",
       y = "Number of Dishes",
       caption = "Source: Kaggle") +
  theme(text = element_text(family = "serif",
                            color = "black"),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 10),
        axis.text.x = element_text(angle = 90,
                                   size = 8,
                                   hjust = .3,
                                   color = "black"
                                   ),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.title = element_text(hjust = .5, 
                                  size=20)
        )
```
